General purpose gene annotation using deep learning

### 2020-01-13 paper/main.tex
minor

\title[short Title]{General purpose gene annotation using deep learning}
\author[Sample \textit{et~al}.]{Felix Stiehler\,$^{\text{\sfb 1,}}$$^\dagger$, Alisandra Denton\,$^{\text{\sfb 1,}}$$^\dagger$\, Marvin Steinborn\,$^{\text{\sfb 1}}$, Andreas Weber\,$^{\text{\sfb 1,}*}$}
\address{$^{\text{\sf 1}}$Institue for Plant Biochemistry, Heinrich-Heine-University, Dusseldorf, D-40225, Germany}

>>>>

\title[short Title]{General purpose gene annotation using deep learning}
\author[Sample \textit{et~al}.]{Felix Stiehler\,$^{\text{\sfb 1,}}$$^\dagger$, Alisandra Denton\,$^{\text{\sfb 1,}}$$^\dagger$\, Marvin Steinborn\,$^{\text{\sfb 1}}$, Stephan Scholz, Andreas Weber\,$^{\text{\sfb 1,}*}$}
\address{$^{\text{\sf 1}}$Institue for Plant Biochemistry, Heinrich-Heine-University, Dusseldorf, D-40225, Germany}
